### 2023-04-12 Notes/nonmonotone_project.tex
Updated Notes/nonmmontone_project.tex

\newcommand{\MAP}{{\text{MAP}}}
\newcommand{\argmax}{{\text{argmax}}}
\newcommand{\argmin}{{\text{argmin}}}
\newcommand{\logistic}{{\text{logistic}}}

@@

    \input{../Tables/monomar_t-5.tex}
    \input{../Tables/monomar_t0.tex}
    \input{../Tables/monomar_t5.tex}

@@

    \input{../Tables/nonmonomar_t-5}
    \input{../Tables/nonmonomar_t0}
    \input{../Tables/nonmonomar_t5}

    \newpage
\end{itemize}

\section*{Todo:}

\begin{itemize}
    \item \textbf{Estimate IPW probabilities for nonmonotone MAR}:
\end{itemize}

>>>>

\newcommand{\MAP}{{\text{MAP}}}
\newcommand{\argmax}{{\text{argmax}}}
\newcommand{\argmin}{{\text{argmin}}}
\newcommand{\Cov}{{\text{Cov}}}
\newcommand{\logistic}{{\text{logistic}}}

@@

    \input{Tables/monomar_t-5.tex}
    \input{Tables/monomar_t0.tex}
    \input{Tables/monomar_t5.tex}

@@

    \input{Tables/nonmonomar_t-5.tex}
    \input{Tables/nonmonomar_t0.tex}
    \input{Tables/nonmonomar_t5.tex}

    While most of these numbers are to be expected, the proposed algorithm
    exhibits considerable bias with the true value of $\theta = -5$. Why does
    this happen? When $\theta = -5$, $p_{21} = \logistic(y_2)$ is very small
    ($\logistic(-5) = 0.007$). This means that in many replications every single
    observation that is initially selected to have $R_2 = 1$ chooses to have
    $R_1 = 0$. I think that this is causing the problem, but I am not totally
    sure how to check.

    \item \textbf{Simulation 2 with Nonmonotone MAR}:
    We also want to simulate data that is correlated. For this simulation, we
    focus on $\Cov(Y_1, Y_2)$. While the probabilities are generated the same as
    the previous simulation the data generating process is

    \[\begin{bmatrix}
    X_i \\ Y_{1i} \\ Y_{2i}
    \end{bmatrix} \stackrel{iid}{\sim}
    N\left(
    \begin{bmatrix}
        0 \\ 0 \\ \theta
    \end{bmatrix},
    \begin{bmatrix}
        1 & 0 & 0 \\
        0 & 1 & \sigma_{yy}\\
        0 & \sigma_{yy} & 1
    \end{bmatrix}
    \right).\]

    We are still interested in $\bar Y_2$ and we still run 1000 simulation with
    1000 observations. In all of the next simulations the true value of $\theta
    = 0$. The results are the following:

    \input{Tables/nonmonomar_t0cy1y20.1.tex}
    \input{Tables/nonmonomar_t0cy1y20.5.tex}
    \input{Tables/nonmonomar_t0cy1y20.9.tex}

    While a small correlation (0.1) in Table 7 (also see Table 5 for no
    correlation), shows that the proposed algorithm with an insignificant level
    of bias, with a stronger correlation the bias increases.
\end{itemize}

{\bf Commments from JK}
\begin{itemize}
    \item Three variables $(X, Y_1, Y_2)$ should be correlated. 
    \item I think the proposed method is doubly robust. So, you may make a
      simulation setup testing DR property. I will explain it further. 
\end{itemize}
